% https://github.com/GoogleCloudPlatform/training-data-analyst/tree/master/courses/ai-for-finance


\section{GCP Finance course}

Took this course from finance
\href{https://github.com/GoogleCloudPlatform/training-data-analyst/tree/master/courses/ai-for-finance}{ai-for-finance}


Modern approaches use Machine Learning
to model fluid market behaviours and complexity.

\begin{itemize}
\item Financial markets are a dynamic, evolving collection of behaviours
\item Use historical data to train a model and adjusts
features and loadings to improve predictive power
\item Integrate the model into an order-execution strategy
\item Retrain and retest continually with new data
to capture the market's current state.
\end{itemize}


Market moves with many human factors that are difficult to measure.

% make into a note
Exogenous and endogenous factors both drive
changes in share prices. Technical strategies tend
to focus on endogenous factors and event-driven
strategies focus on exogenous factors.

% 04 04_what-do-we-want-to-model-lets-start-simple.mp4


% quant strategies
 Strategies range
from low-frequency, at least by trading
standards, to high-frequency. You must implement high-frequency
trading strategies with software and market
interfaces that can handle sub-millisecond order
creation and submission. Quant strategies
are also a type of forecasting method that
attempts to predict the future value of a stock or other instrument where
the direction of a price spread between
two instruments. These forecasts are based on an observed price response
to factors that you have identified as
statistically significant in predicting changes in
an instrument's price. Mean reversion strategies
depend on the stability or stationarity of an asset's price or spread relative
to another asset. When the price risk
spread gets too high, it becomes more likely
that it will decrease, and so revert to its long-term
mean or neutral value. When the price risk
spread gets too low, it becomes more likely
that it will increase, and again revert to its mean. Correlation is a
measure of how well two variables move
together over time.
